The paper on \Large \bf Blockchain Frontrunning

### 2018-09-06 frontrunning/Latex/setup/table.tex
[frontrunning] update dapps table and bib

\begin{table}[t]
\centering
\begin{tabular}{|c|c|}
\hline
\textbf{DApp Category}    											& \textbf{DApp Names (Rank)} \\  \hline
\multirow{6}{*}{Exchanges} 										& IDEX (1) \\ 
															& ForkDelta, EtherDelta (2) \\
															& \textbf{Bancor (7)} \\
															& The Token Store(13) \\
															& LocalEthereum(14) \\
															& Kyber (22) \\  \hline

@@

\multirow{6}{*}{Gambling}											& Fomo3D (5) \\  
															& DailyDivs (6) \\ 
															& FomoWar (10) \\
															& FairDapp (11)\\
															& Zethr(17) \\
															& dice2.win (20) \\
															& Kyber (22) \\  \hline

\multirow{2}{*}{\shortstack{High-Risk \\ (Ponzi Schemes and Lotteries)}}		& PoWH 3D (8)	 \\ 
															& Ether Shrimp Farm(21) \\  \hline

\multirow{2}{*}{Misc}												& 0x Protocol (23) \\
															& \textbf{Ethereum Name Service (24)}  \\  \hline

\end{tabular}
\caption{\footnotesize{Top 25 DApps based on recent user activity from \texttt{Dappradar.com}.}\label{tab:top25dapps}}
\end{table}
% ------------------------------------------------------------------------------------------------------------------------------------------------%

>>>>

\begin{table}[t]
\centering
\begin{tabular}{|c|c|}
\hline
\textbf{DApp Category}    											& \textbf{DApp Names (Rank)} \\  \hline
\multirow{6}{*}{Exchanges} 										& IDEX (1) \\ 
															& ForkDelta, EtherDelta (2) \\
															& \textbf{Bancor (7)} \\
															& The Token Store(13) \\
															& LocalEthereum(14) \\
															& 0x Protocol (23) \\
															& Kyber (22) \\  \hline

@@

\multirow{6}{*}{Gambling}											& Fomo3D (5) \\  
															& DailyDivs (6) \\ 
															& FomoWar (10) \\
															& FairDapp (11)\\
															& Zethr(17) \\
															& dice2.win (20) \\ 
															& PoWH 3D (8)	 \\ 
															& Ether Shrimp Farm(21) \\  \hline

\multirow{2}{*}{Name Services}												
															& \textbf{Ethereum Name Service (24)}  \\  \hline

\end{tabular}
\caption{\footnotesize{Top 25 DApps based on recent user activity from \texttt{Dappradar.com} on September 4th, 2018.}\label{tab:top25dapps}}
\end{table}
% ------------------------------------------------------------------------------------------------------------------------------------------------%
